### 2014-01-21 abstract.tex
abstract.tex edited online with Bitbucket

\section*{Abstract}
Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second leading cause of cancer-related death.
Multi-parametric Magnetic Resonance Imaging (mpMRI) has gained recent
popularity to characterize PCa.  ARFI imaging has the potential to aid in PCa
diagnosis and management by evaluating the structural composition of prostate
zones and tumors based on their stiffness.  In this study, MR and ARFI imaging
datasets were compared to one another and with gross pathology measurements
made immediately post radical prostatectomy.  Images were manually segmented to
delineate the central gland (CG) and prostate capsule, and 3D models were
rendered to evaluate zonal anatomy dimensions and volumes.  Both imaging
modalities showed moderate correlations between estimated organ volume and
gross pathologic weights.  ARFI and MR total prostate gland volumes were
well-correlated (R$^2$ = 0.63), but ARFI images yielded prostate volumes that
were, on average, larger (6.1\% $\pm$ 25\%) than MR images, primarily due to
over-estimation of the lateral dimension of the total gland
(\ARFImrTotalLatLatMeanPct $\pm$ \ARFImrTotalLatLatStdPct\%), while
over-estimates of the other dimensions were less significant
(\ARFImrTotalAntPostMeanPct $\pm$ \ARFImrTotalAntPostStdPct\% and
\ARFImrTotalApexBaseMeanPct $\pm$ \ARFImrTotalApexBaseStdPct\%).  The ARFI and
MR CG volumes were also moderately correlated (R$^2$ = 0.38).  CG volume
differences were attributed to under-estimation of the apex-to-base axis
(\ARFImrCentralApexBaseMeanPct $\pm$ \ARFImrCentralApexBaseStdPct\%), and
over-estimation bias in the lateral dimension (\ARFImrCentralLatLatMeanPct
$\pm$ \ARFImrCentralLatLatStdPct\%).  ARFI prostate imaging yielded prostate
volumes and dimensions that were correlated with MR T2WI estimates, with biases
in the AP dimension, most likely related to poor displacement SNR in the
anterior region of the prostate from greater distance from the rectal wall
imaging surface.  Lateral dimension contrast was also challenging due to
peri-prostatic fat.  ARFI imaging is a promising low-cost, real-time imaging
modality that can compliment MR imaging for diagnosis, treatment planning and
management of PCa.

>>>>

\section*{Abstract}
Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second leading cause of cancer-related death.
Two imaging modalities, Multi-parametric Magnetic Resonance Imaging (mpMRI) and
Acoustic Radiation Force Imaging have the potential to aid in PCa
diagnosis and management by evaluating the structural composition of prostate
zones and tumors based on water content and stiffness respectively.  In this study, 
MR and ARFI imaging datasets were compared to one another and against gross pathology.  
MR and ARFI images were manually segmented in 3D Slicer to delineate the central gland (CG) and prostate capsule. 3D
models were then rendered in 3D Slicer to evaluate zonal anatomy tri-axial dimensions and
volumes.  Both imaging modalities showed moderate correlations between
estimated organ volume and gross pathologic weights.  In terms of intra-modality comparison,
ARFI and MR total prostate gland volumes were well-correlated (R$^2$ = \MRarfiVolTotalRsq), but
ARFI yielded prostate volumes that were, on average, larger
(\MRarfiVolTotalMeanDiff\% $\pm$ \MRarfiVolTotalStdDiff\%) than MR. This was
primarily due to total gland over-estimation along the lateral dimension.
(\ARFImrTotalLatLatMeanPct $\pm$ \ARFImrTotalLatLatStdPct\%). Differences between MR and
ARFI in the other dimensions were less significant (\ARFImrTotalAntPostMeanPct $\pm$
\ARFImrTotalAntPostStdPct\% and \ARFImrTotalApexBaseMeanPct $\pm$
\ARFImrTotalApexBaseStdPct\%). ARFI and MR CG volumes were also
well-correlated (R$^2$ = \MRarfiVolCentralRsq).  CG volume differences were
attributed to apex-to-base axis underestimation by MR
(\ARFImrCentralApexBaseMeanPct $\pm$ \ARFImrCentralApexBaseStdPct\%), and
lateral dimension over-estimation by ARFI (\ARFImrCentralLatLatMeanPct
$\pm$ \ARFImrCentralLatLatStdPct\%).  Overall, ARFI prostate imaging yielded prostate
volumes and dimensions that were correlated with MR T2WI estimates, with biases
in the lateral dimension, most likely related to poor displacement SNR in the
anterior region of the prostate from greater distance from the rectal wall
imaging surface. (I don't agree with this statement, our anterior to potsterior dimensions correlations were good)  Lateral dimension contrast was also challenging due to
peri-prostatic fat.  ARFI imaging is a promising low-cost, real-time imaging
modality that can compliment mpMRI for diagnosis, treatment planning and
management of PCa.
